---
title: "Alcohol vs Seat choice"
author: "Kevin Ortega"
date: "Fall 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv" )
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??


## Now with ggplot - first select the basic data

$H_0$ : there is no difference between amount of alcohol consumed and where you sit.

$H_A$ : There is a difference between the amount of alcohol consumed and where you sit.

Alcohol is numerical,
Seat is categorical.

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
  


  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```
The box plot shows us that the consumption of alcohol for those in the back seats is the highest, while those in the middle consumed less, but more than those who consumed the least in the front seats.
## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```
The average of the ounces consumed for those seated in the back would be 8.5, while those seated in the front have an average of 1.7 and those in the middle consumed and consumed and average of 3.3 ounces of alcohol.

## Inferential Tests

```{r}
model1 <-aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

The P-value is 0.000116 which is lower than 0.05, which causes us to reject the null hypothesis.

```{r}
plot(TukeyHSD(model1))
```

The tukey shows that both front-back and middle-back are different, but in the middle-front is not different. 

## Conclusions

The boxplot showed us that those in the back seat consumed the most amount of alcohol while those in the middle seats consume less than them and those seated in the front consumed the least amount of alcohol. Then the numericalsummary showed us how the average of ounces of alcohol consumed by the people in the back seats is 8.5, average consumed by those in the front seat is 1.7 and finally those in the middle class seats consumed and average of 3.3 ouncees of alcohol. The P-Value in inferential tests is 0.000116 which is lower than 0.05. We then reject the null hypothesis since there is diference in alcohol consumption based on where sit.

